\documentclass[titlepage]{article}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{draftwatermark}

\SetWatermarkText{Draft}
\SetWatermarkScale{10}

\pagestyle{fancy}
\lhead{The School System for Student-Centered Learning}
\rhead{Made by r/StudentCenteredLearin}
\cfoot{Page \thepage\ of \pageref{LastPage}}

\setcounter{secnumdepth}{4}
\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}


\author{r/StudentCenteredLearin}
\title{The School System for Student-Centered Learning}
\date{February 23, 2022 - ?}
\begin{document}
\maketitle
\newpage
\tableofcontents
\newpage
\section{Introduction}
An introduction to The School System for Student-Centered Learning
\subsection{The importance of school}
Here we talk about why school is important
\subsection{What is wrong with the current school system?}
Here we address the general problems with the current school systems


\newpage
\section{The School System for Student-Centered Learning}
Here we explain what we are going to talk about in this section
\subsection{Our main goal}
Here we explain the main goal of The School System for Student-Centered Learning
\subsection{How are we going to achieve this goal?}
Here we talk about how we are going to achieve our main goal

\newpage
\section{Rules}
Here we explain why we did not like the current rules of the current school system.
\subsection{Rules}
\begin{enumerate}
	\item Example rule 1
	\item Example rule 2
	\item Example rule 3
\end{enumerate}
\subsection{Reasons}
Here we explain each rule

\newpage
\section{Subjects}
Here we explain what we are going to talk about in this section
\subsection{Mandatory subjects 4-10}
Here we list out all the mandatory subjects for kids aged 4-10 years old
\subsection{Extra subjects 4-10}
Here we list out all the extra subjects for kids aged 4-10 years old
\subsection{Mandatory subjects 11-18}
Here we list out all the mandatory subjects for kids aged 11-18 years old
\subsection{Extra subjects 11-18}
Here we list out all the extra subjects for kids aged 11-18 years old
\subsection{Reasoning age 4-10}
Here we explain why we choose for the mandatory and extra subjects for kids aged 4-10.
\subsection{Reasoning age 11-18}
Here we explain why we choose for the mandatory and extra subjects for kids aged 11-18.

\newpage
\section{Country Specific}
Here we explain why we have country specific and how we are going to implement it into our school system.

\subsection{Belgium}
Here we talk about country specific things for Belgium.
\subsubsection{Subjects}
Here we list all the subjects that are not in the Subjects chapter, but we do want to have in Belgium.
\paragraph{History}
Here we talk about specific history for Belgium.

\subsection{France}
Here we talk about country specific things for France.
\subsubsection{Subjects}
Here we list all the subjects that are not in the Subjects chapter, but we do want to have in France.
\paragraph{History}
Here we talk about specific history for France.

\subsection{Germany}
Here we talk about country specific things for Germany.
\subsubsection{Subjects}
Here we list all the subjects that are not in the Subjects chapter, but we do want to have in Germany.
\paragraph{History}
Here we talk about specific history for Germany

\subsection{The Netherlands}
Here we talk about country specific things for the Netherlands.
\subsubsection{Subjects}
Here we list all the subjects that are not in the Subjects chapter, but we do want to have in the Netherlands.
\paragraph{History}
Here we talk about specific history for the Netherlands.

\subsection{Spain}
\subsubsection{Subjects}
Here we list all the subjects that are not in the Subjects chapter, but we do want to have in Spain.
\paragraph{History}
Here we talk about specific history for Spain

\subsection{United States of America}
Here we talk about country specific things for United States of America.
\subsubsection{Subjects}
Here we list all the subjects that are not in the Subjects chapter, but we do want to have in United States of America.
\paragraph{History}
Here we talk about specific history for United States of America

\newpage
\section{School times}
Here we explain from what time to what time kids will go to school

\newpage
\section{Credits}
\subsection{Original idea}
Kevin Giesberts
\subsection{Introduction}
Everybody who helped write the introduction.
\subsection{Rules}
Everybody who helped develop the rules.
\subsection{Grammar}
Everybody who helped checking grammar.
\subsection{Other helpers}
Stephen van Erkelens
\newline
Prestigious\_Note1475
\newline
Dustractor

\newpage
\section{Sources}
All sources used to develop the school system.
\subsection{Introduction}
All sources used to write the introduction
\subsection{Rules}
All sources used to write the rules
\end{document}
\end{document}
